---
title: "Simple document"
output: github_document

    
---
```{r,echo=FALSE, message=FALSE}
library(tidyverse)
library(patchwork)
library(p8105.datasets)
```

#let's begin
```{r}
library(tidyverse)
library(modelr)
library(mgcv)
```
```{r}
set.seed(1)
```

#problem2
Create a _city_state_ variable (e.g. “Baltimore, MD”), and _a binary variable_ indicating whether the homicide is solved. 
```{r}
homicide = read.csv("./homicide-data.csv") 

homicide=homicide%>% 
  na.omit() %>% 
  mutate(
    city_state=str_c(city,",",state)
  ) %>% 
  mutate(solve_sit = case_when(
    disposition== "Closed by arrest" ~ 1,
    disposition== "Open/No arrest" ~ 0)) %>% 
 mutate(
   unsolved = case_when(
     disposition== "Closed by arrest" ~ 0,
    disposition== "Open/No arrest" ~ 1))%>% 
  na.omit() 
                          
```



Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. For this problem, limit your analysis those for whom victim_race is white or black. Be sure that victim_age is numeric.

```{r}
homicide =homicide%>% 
filter(!city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")) %>% 
  filter(str_detect(victim_race, c("White", "Black"))) %>% 
  mutate(victim_age =as.numeric(victim_age))%>% 
  na.omit()
```
