---
title: "Simple document"
output: github_document

    
---
```{r,echo=FALSE, message=FALSE}
library(tidyverse)
library(patchwork)
library(p8105.datasets)
```

#let's begin
```{r}
library(tidyverse)
library(modelr)
library(mgcv)
```
```{r}
set.seed(1)
```

#problem2
Create a _city_state_ variable (e.g. “Baltimore, MD”), and _a binary variable_ indicating whether the homicide is solved. 
```{r}
homicide = read.csv("./homicide-data.csv") 

homicide=homicide%>% 
  na.omit() %>% 
  mutate(
    city_state=str_c(city,",",state)
  ) %>% 
  mutate(solve_sit = case_when(
    disposition== "Closed by arrest" ~ 1,
    disposition== "Open/No arrest" ~ 0)) %>% 
 mutate(
   unsolved = case_when(
     disposition== "Closed by arrest" ~ 0,
    disposition== "Open/No arrest" ~ 1))%>% 
  na.omit() 
                          
```



Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. For this problem, limit your analysis those for whom victim_race is white or black. Be sure that victim_age is numeric.

```{r}
homicide =homicide%>% 
filter(!city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")) %>% 
  filter(str_detect(victim_race, c("White", "Black"))) %>% 
  mutate(victim_age =as.numeric(victim_age))%>% 
  na.omit()
```

For the city of Baltimore, MD, use the glm function to fit a logistic regression with _resolved vs unresolved_ as the outcome and _victim_ _age_, _sex_ and _race_ as predictors. Save the output of glm as an R object; 
```{r}
data_B= filter(homicide,city_state=="Baltimore,MD")
data_B_model = data_B%>% 
  glm(solve_sit ~ victim_age + victim_race + victim_sex, data = ., family = binomial())

data_B_model %>% 
  broom::tidy(conf.int = TRUE) %>% 
  mutate(OR = exp(estimate), 
  conf_low=exp(estimate-1.96*std.error), 
  conf_high=exp(estimate+1.96*std.error)
  ) %>%
  select(term, log_OR = estimate, OR, p.value, conf_low, conf_high) %>% 
  knitr::kable(digits = 3)
##
exp(summary(data_B_model)$coefficients["victim_sexMale",1] + qnorm(c(0.025,0.5,0.975)) * summary(data_B_model)$coefficients["victim_sexMale",2])
```
Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.
```{r}
all_city_model = 
  homicide %>%
  nest(data = -city_state) %>% 
  mutate(
    logmodel = map(data, ~glm(solve_sit~victim_age + victim_race + victim_sex, family = binomial(), data = ., )),
     result = map(.x=logmodel, ~broom::tidy(.x,conf.int = TRUE))) %>% 
  select(-data,-logmodel)%>% 
  unnest(result)%>% 
  mutate(
    OR = exp(estimate), 
    conf_low=exp(estimate-1.96*std.error), 
    conf_high=exp(estimate+1.96*std.error)
    ) %>%
  select(city_state,term, log_OR = estimate, OR, p.value, conf_low, conf_high) %>% 
  filter(term == "victim_sexMale")
```
```{r}
all_city_model%>%
  mutate(
    city_state = fct_reorder(city_state, OR)
  ) %>%
  ggplot(aes(x = OR, y = city_state)) +
  geom_point() +
  geom_errorbar(aes(xmin = conf_low, xmax = conf_high)) +
  labs(title = "OR of solved cases for male and female victims",
       x="City_state",
       y="Odds_ratio"
         )
```

#problem3
Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).

Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.
```{r}
data_bw <- read.csv("./birthweight.csv")%>% 
  na.omit() %>% 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace), 
    malform = as.factor(malform),
    mrace = factor(mrace)
    )
  
data_bw %>% 
  ggplot(aes(x = bhead, y = bwt)) + 
  geom_point(alpha = .5)+
  ylab("Baby weight at birth") +
  xlab("Baby head circumference at birth") +
  labs(title = "plot of baby weight vs baby head circumference at birth")
```
